\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{microtype}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!70!black,
    urlcolor=blue!70!black,
    citecolor=blue!70!black,
}

\pagestyle{fancy}
\fancyhf{}
\rhead{KRAKEN Bug Reports}
\lhead{SRSE 2026 -- Mahadi Hasan}
\rfoot{\thepage}

\title{\textbf{Bug Reports for the paper:\\
\textit{KRAKEN: Program-Adaptive Parallel Fuzzing}}}
\author{Mahadi Hasan \\ \small UIUC SRSE 2026}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{fancy}


\tableofcontents
\newpage

%----------------------------------------------------------------------
\section{Introduction}

\textit{KRAKEN: Program-Adaptive Parallel Fuzzing} (ISSTA 2025,
\url{https://dl.acm.org/doi/10.1145/3728882}), presents a new program-adaptive parallel
fuzzer. As part of evaluating KRAKEN's effectiveness, the authors ran it against 37
popular open-source projects and reported the following results:
\begin{itemize}[nosep]
    \item \textbf{192 bugs} found across 37 real-world projects
    \item \textbf{119 CVE IDs} assigned to those bugs
\end{itemize}
These bugs were reported to the developers of the affected software, typically as GitHub
issues or pull requests (but also via Bugzilla, SourceForge, and mailing lists).

%----------------------------------------------------------------------
\section{Search Process}

The overall strategy is illustrated in Figure~\ref{fig:flowchart}. Two independent paths
are run in parallel and then joined on the bug report URL to produce the final dataset.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
  node distance = 0.6cm and 1.6cm,
  start/.style   = {rectangle, rounded corners=4pt, draw=gray!70, fill=gray!12,
                    text width=4.2cm, align=center, minimum height=0.75cm, font=\small},
  cvebox/.style  = {rectangle, draw=blue!60!black, fill=blue!9,
                    text width=4.2cm, align=center, minimum height=0.75cm, font=\small},
  authbox/.style = {rectangle, draw=green!50!black, fill=green!8,
                    text width=4.2cm, align=center, minimum height=0.75cm, font=\small},
  joinbox/.style = {rectangle, rounded corners=4pt, draw=purple!60!black, fill=purple!8,
                    text width=4.2cm, align=center, minimum height=0.75cm, font=\small},
  ok/.style      = {rectangle, rounded corners=3pt, draw=green!55!black, fill=green!10,
                    text width=9cm, align=center, minimum height=0.75cm, font=\small},
  arr/.style     = {-Stealth, thick},
  cvearr/.style  = {-Stealth, thick, blue!65!black},
  autharr/.style = {-Stealth, thick, green!55!black},
  joinarr/.style = {-Stealth, thick, purple!60!black},
]

%% ── Shared source ─────────────────────────────────────────────────
\node[start] (readme) {KRAKEN GitHub README\\119 CVE IDs (Trophy section)};

%% ── CVE path (left) ───────────────────────────────────────────────
\node[cvebox, below left=1.4cm and 2.3cm of readme] (json)
    {CVEProject/cvelistV5\\fetch JSON per CVE ID};
\node[cvebox, below=of json] (refs)
    {Extract \texttt{references} field\\$\rightarrow$ bug report URL\\
     {\small\textbf{117\,/\,119 CVEs resolved}}};

%% ── Author path (right) ───────────────────────────────────────────
\node[authbox, below right=1.4cm and 2.3cm of readme] (identity)
    {Author: Anshunkang Zhou\\
     \texttt{seviezhou} (GitHub/Trac)\\
     \texttt{azhouad} (SourceForge)};
\node[authbox, below=of identity] (platforms)
    {Query by author identity:\\
     GitHub · Trac · SourceForge\\
     Red Hat Bugzilla};

%% ── Join ──────────────────────────────────────────────────────────
\node[joinbox, below=2.8cm of readme] (join)
    {JOIN on \texttt{bug\_url}\\(normalize, left join)};

%% ── Output ────────────────────────────────────────────────────────
\node[ok, below=0.6cm of join] (out)
    {\textbf{188 bug reports} across 31 of 37 KRAKEN projects
     \quad|\quad 113 bugs linked to a CVE (105 unique CVEs) \quad|\quad 75 without CVE};

%% ── Arrows ────────────────────────────────────────────────────────
\draw[cvearr]  (readme) -- node[above,sloped,font=\small]{CVE IDs} (json);
\draw[cvearr]  (json)   -- (refs);
\draw[cvearr]  (refs)   -- (join);

\draw[autharr] (readme)   -- node[above,sloped,font=\small]{author query} (identity);
\draw[autharr] (identity) -- (platforms);
\draw[autharr] (platforms) -- (join);

\draw[joinarr] (join) -- (out);

%% ── Background shading ────────────────────────────────────────────
\begin{scope}[on background layer]
  \node[inner sep=9pt, fill=blue!4, draw=blue!25, rounded corners,
        fit=(json)(refs)] {};
  \node[inner sep=9pt, fill=green!4, draw=green!25, rounded corners,
        fit=(identity)(platforms)] {};
\end{scope}

\end{tikzpicture}
\caption{Search process for locating KRAKEN bug reports.
  \textcolor{blue!55!black}{\textbf{Blue:}} CVE-based path --- 119 CVE IDs fetched from
  the CVEProject JSON database; 117 bug report URLs resolved.
  \textcolor{green!45!black}{\textbf{Green:}} Author-based path --- bug tracker accounts
  of the first author queried across GitHub, FFmpeg Trac, SourceForge, and Bugzilla.
  \textcolor{purple!60!black}{\textbf{Purple:}} Results joined on \texttt{bug\_url} to
  produce the final dataset of 188 unique bug reports across 31 of 37 KRAKEN projects.}
\label{fig:flowchart}
\end{figure}

\paragraph{Step 1 --- KRAKEN GitHub README.}
The KRAKEN repository at \url{https://github.com/seviezhou/Kraken} contains a Trophy
section in its \texttt{README.md} listing all 119 CVE IDs. These serve as the input for
the CVE-based path.

\paragraph{Step 2 --- CVE JSON lookup (blue path).}
Each CVE ID maps to a JSON record in the \texttt{CVEProject/cvelistV5} GitHub repository.
The path is derived mechanically from the CVE year and numeric prefix:

\begin{center}
\small\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}ll@{}}
\toprule
CVE ID   & \texttt{CVE-2021-39550} \\
JSON URL & \href{https://raw.githubusercontent.com/CVEProject/cvelistV5/main/cves/2021/39xxx/CVE-2021-39550.json}{\texttt{.../cves/2021/39xxx/CVE-2021-39550.json}} \\
\midrule
\texttt{references} field & \url{https://github.com/sahaRatul/sela/issues/30} \\
\bottomrule
\end{tabular}
\end{center}

\noindent The \texttt{references} field yields the upstream bug report URL.
This step resolved \textbf{117 out of 119 CVEs} (2 records absent from the database).

\paragraph{Step 3 --- Author-based tracker search (green path).}
The first author, Anshunkang Zhou, operates under different identities across platforms.
Each tracker is queried directly by those identifiers:

\begin{center}
\small\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Platform} & \textbf{Identifier} & \textbf{Method} \\
\midrule
GitHub            & \texttt{seviezhou}    & Search API: \texttt{author:seviezhou type:issue} \\
FFmpeg Trac       & \texttt{seviezhou}    & \texttt{/query?reporter=seviezhou\&format=tab} \\
SourceForge       & \texttt{azhouad}      & Per-ticket fetch on giflib, gocr, fig2dev \\
Red Hat Bugzilla  & Anshunkang Zhou       & Known bug IDs confirmed by acknowledgment \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Step 4 --- Join.}
The two result sets are joined on the bug report URL (after stripping any
\texttt{\#fragment} suffix). A left join from the author-search results onto the CVE
records attaches a CVE ID to each bug where one exists, leaving the field blank otherwise.
The final dataset contains \textbf{188 bug reports} across 31 of 37 KRAKEN projects: 113 with a CVE ID and 75 without.

%----------------------------------------------------------------------
\section{Summary by Project}
\label{sec:summary}

Table~\ref{tab:summary} summarises all projects where bug reports were filed by the paper's
first author (Anshunkang Zhou), derived by joining the author's bug tracker activity with
the KRAKEN CVE assignments. \textbf{Bugs Filed} is the total number of issues opened;
\textbf{With CVE} counts those that received a CVE ID; \textbf{Without CVE} counts the
remainder.

\input{generated/table_summary}

\noindent\textbf{Notes:}
\begin{itemize}[nosep]
    \item ffmpeg has 1 CVE but that CVE references 3 separate Trac tickets (\#8845, \#8859, \#8860).
    \item gpac and libredwg each report 9 CVEs; one CVE per project could not be fetched from
          the CVEProject database (\texttt{CVE-2020-23927} and \texttt{CVE-2020-20817} respectively).
    \item 4 projects (\texttt{asn1c}, \texttt{libelfin}, \texttt{libnsfdb}, \texttt{libraw}) have 0 confirmed CVEs, accounting for 11 bugs with no CVE link.
\end{itemize}

%----------------------------------------------------------------------
\section{Detailed Bug Report Links}
\label{sec:links}

All bug reports in Table~\ref{tab:cves} were filed by \textbf{Anshunkang Zhou}, the paper's
first author, who operates under the following identifiers across platforms:
\begin{itemize}[nosep]
    \item \textbf{GitHub / FFmpeg Trac:} \texttt{seviezhou}
    \item \textbf{SourceForge:} \texttt{azhouad}
    \item \textbf{Red Hat Bugzilla:} Anshunkang Zhou (real name)
\end{itemize}

The table is derived by joining the author's bug tracker activity with the KRAKEN CVE
assignments and is grouped by project. Rows with a CVE ID link to the corresponding
CVEProject JSON record; rows without one show ``---''. Where a single CVE references
multiple upstream tickets (e.g.\ ffmpeg), one row is added per ticket.

\input{generated/table_cves}

\subsection*{CVE-Referenced Reports Not Found in Author Search}
\label{sec:orphans}

Table~\ref{tab:orphans} lists bug reports that appear in CVEProject JSON records but were
absent from the author's live bug tracker activity. Each entry falls into one of two categories:

\begin{itemize}[nosep]
    \item \textbf{Deleted issues} --- the bug report existed at the time the CVE was filed
          but has since been removed from the tracker.
    \item \textbf{Unverifiable authorship} --- the issue is still accessible but could not
          be confirmed as filed by Anshunkang Zhou under any of the known identifiers
          (\texttt{seviezhou}, \texttt{azhouad}, real name).
\end{itemize}

\input{generated/table_orphan_cves}

%----------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

Table~\ref{tab:comparison} compares per-project bug and CVE counts from the KRAKEN supplement
material (Table~1) against what this pipeline was able to confirm.
Overall, the pipeline recovered \textbf{188 of the 192 bug reports} and confirmed
\textbf{105 of the 117 resolvable CVEs}.

\paragraph{Why 105 confirmed CVEs, not 117.}
Of the 119 CVE IDs listed in the KRAKEN trophy section, two
(\texttt{CVE-2020-23927} and \texttt{CVE-2020-20817}) have no record in the CVEProject
database, leaving 117 resolvable CVEs.
Of those, \textbf{105 unique CVEs} were traced to bug reports found in the author search
(Table~\ref{tab:cves}).
Because some CVEs reference multiple tickets --- e.g.\ \texttt{CVE-2020-24995} covers three
FFmpeg Trac tickets, and several gocr CVEs appear in both SourceForge and Bugzilla ---
the 105 confirmed CVEs expand to \textbf{113 rows} in Table~\ref{tab:cves}.
The remaining \textbf{12 unique CVEs} are represented in Table~\ref{tab:orphans} as 13 rows
(one ncurses CVE references two separate mailing-list posts).
Taken together: $105 + 12 = 117$ unique CVEs accounted for.

\paragraph{Why 188 bugs, not 192.}
The net gap of 4 is the result of two opposing effects, not a simple shortfall.
Six KRAKEN projects returned zero results in the author search, collectively accounting for
18 missing bugs:
\begin{itemize}[nosep]
  \item \texttt{advancecomp} (3), \texttt{jhead} (2), \texttt{nasm} (2), \texttt{sox} (3) ---
        no tracker activity found under any known author identifier.
  \item \texttt{ncurses} (2), \texttt{pdftools} (6) --- bugs exist in CVE JSON references
        (Table~\ref{tab:orphans}) but could not be confirmed in the live author search.
\end{itemize}
Against this, five projects returned \emph{more} results than the paper claims, adding
14 extra bugs: \texttt{dmg2img} ($+2$), \texttt{gocr} ($+3$), \texttt{libslax} ($+1$),
\texttt{retdec} ($+7$), \texttt{sela} ($+1$).
These likely reflect issues filed by the same author outside the paper's experiment window.
The net effect is $192 - 18 + 14 = 188$.

\input{generated/table_comparison}

%----------------------------------------------------------------------
\end{document}